Sequential hypothesis testing allows data collection to continue until sufficient evidence
accumulates, offering flexibility over fixed-sample designs.
A key challenge, however, is that stopping rules which trigger on decision criteria,
such as p-value thresholds or posterior-based heuristics, can introduce confirmation
bias through early peeking on unrepresentative samples.
Methods that decouple the stopping criterion from the decision criterion, such as
``Precision is the Goal'' (PitG), eliminate this bias by halting only once a target
posterior precision is reached.
Yet we show that PitG frequently yields inconclusive outcomes, most notably when the
null hypothesis is true.
To address this, we propose ``Decisive Precision is the Goal'' (DPitG), which requires
both the precision target and a decisive hypothesis outcome (i.e., accept or reject the null)
to be met simultaneously before stopping.
In fair coin experiments ($\theta_{\rm true}= \theta_{\rm null}=0.5$,
equivalence region width $0.10$ and precision goal of
$\omega_{\rm goal}=0.08$), PitG yields
$63.3\%$ inconclusive outcomes; DPitG reduces this to just $2.3\%$,
with only a $4.7\%$ increase in median sample size.
Moreover, DPitG's conclusiveness remains essentially flat ($0.972$--$0.979$)
across a broad range of precision goals ($\omega_{\rm goal}=0.06$--$0.10$),
while PitG's conclusiveness spans from $82.5\%$ to $0\%$ (entirely inconclusive
at the loosest setting), demonstrating DPitG's robustness to the choice of $\omega_{\rm goal}$.
This advantage of high conclusiveness, zero false-positive rate, and modest sample cost 
holds broadly across $\theta_{\rm true}$ and $\theta_{\rm null}$ values.
%More broadly, unlike methods that can only reject the null hypothesis, the
%precision-based framework also permits its positive acceptance ---
%a property it retains with a near-zero false-positive rate: exactly zero when
%$\theta_{\rm true}=\theta_{\rm null}$ and negligibly small near the equivalence boundary.
We provide a closed-form sample-size planning formula,
an online interactive calculator, and open-source code to support the planning
and interpretation of sequential experiments.

%%TODO: note that the phrasing of "nlike methods that can only reject the null hypothesis, the precision-based framework also permits its positive acceptance" are 
%% a bit decieinvg, b/c, e.g, Bayes Factors can also accept the null, but only when the data are extremely strong, whereas the precision-based framework can accept the null when the data are sufficiently precise, which is a more common occurrence.

%% -----------------------------------------------------------------------
%% IMRaD ALTERNATIVE (for reference)
%% -----------------------------------------------------------------------
% \textbf{Background.} Sequential hypothesis testing offers flexibility over
% fixed-sample designs, but risks confirmation bias when stopping rules are
% coupled to decision criteria.
%
% \textbf{Gap.} Existing decoupled approaches such as ``Precision is the Goal''
% (PitG) eliminate this bias but produce high rates of inconclusive outcomes,
% especially when the null hypothesis is true.
%
% \textbf{Method.} We propose ``Decisive Precision is the Goal'' (DPitG), which
% requires both a target posterior precision and a conclusive hypothesis outcome
% to be satisfied simultaneously before stopping.
%
% \textbf{Results.} In fair coin simulations ($\theta_{\rm true}=0.5$,
% $\omega_{\rm goal}=0.08$), PitG yields 63.3\% inconclusive outcomes; DPitG
% reduces this to 2.3\% with only a 4.7\% median increase in sample size,
% while preserving zero false positives.
%
% \textbf{Impact.} DPitG offers a practical and principled solution for sequential
% testing when decisive outcomes are required. Open-source code and an interactive
% calculator are provided.
%% -----------------------------------------------------------------------
