While the present study focuses on single-group Bernoulli data, the HDI+ROPE
precision-goal framework extends naturally to single-group continuous outcomes and
two-group comparisons (both binomial and continuous); see Appendix~\ref{app:extensions}
for the adaptations and corresponding sample-size planning equations.

ePitG operates under a different philosophy from classical sequential methods.
Group sequential designs \citep{jennison2000} control the familywise Type~I error rate
across interim analyses via alpha-spending functions, and are therefore tied to the
number and timing of planned looks.
ePitG requires no such correction, since the Bayesian posterior accounts for all
accumulated data without reference to the stopping intention.
Closest in spirit among Bayesian sequential designs is Bayes Factor Design Analysis
(BFDA) \citep{schonbrodt2018}, which plans sample size to achieve a target Bayes Factor
with specified probability.
% \citet{schonbrodt2018}: Sch\"onbrodt \& Wagenmakers (2018) introduce BFDA as the
% natural Bayesian sequential counterpart to power analysis: it targets evidential
% strength (Bayes Factor) rather than posterior precision, making it complementary to
% rather than competing with ePitG.
The key distinction is that BFDA targets evidential strength (ratio of marginal
likelihoods) whereas ePitG targets posterior precision; the two are complementary,
and a design requiring both a conclusive HDI+ROPE verdict and a minimum Bayes Factor
is a natural extension.

A practical advantage worth stating explicitly is that, for models with conjugate or
tractable posteriors --- including all settings studied or discussed in this paper ---
ePitG requires no MCMC at runtime.
For Bernoulli data the posterior is a Beta distribution updated in closed form after
each observation, and the HDI is computed analytically.
The entire algorithm reduces to a short loop requiring only standard statistical
functions, with no specialist probabilistic programming software.
This low implementation barrier makes ePitG immediately accessible to any analyst
working in Python, R, or a spreadsheet environment.
Non-conjugate priors or hierarchical models would require MCMC, but such settings
fall outside the scope of the present work.
% More precisely, the no-MCMC claim holds case by case as follows:
% - Single-group Bernoulli (this paper): conjugate Beta posterior, fully analytical
%   HDI; no sampling of any kind needed.
% - Single-group continuous (conjugate normal prior): normal or Student-t posterior,
%   fully analytical; no MCMC needed.
% - Two-group binomial: no closed form for the difference of two Betas, but
%   direct i.i.d. Monte Carlo suffices (draw from Beta_1, draw from Beta_2, subtract);
%   this is plain Monte Carlo, not a Markov chain.
% - Two-group continuous (weakly informative prior): by the Bernstein--von Mises
%   theorem the posterior converges to a normal, so Welch's standard error gives the
%   HDI width without sampling.
% - Non-conjugate informative priors: MCMC would be required; this case is deferred
%   to future work.
% - Hierarchical models: MCMC required; also out of scope here.

These implementation properties complement the broader methodological advantages of
the HDI+ROPE framework.
A practical advantage of the HDI+ROPE framework over frequentist approaches concerns
multiple comparisons. In NHST, conducting several tests simultaneously inflates the
Type~I error rate, requiring corrections (e.g.\ Bonferroni) that reduce the power of
each individual test. Frequentist confidence intervals inherit the same dependence on
the full set of intended comparisons, since their coverage properties are tied to
p-values. Consequently, both power and precision planning must account for the number
of planned tests.

The Bayesian posterior is not affected in this way. Because the posterior distribution
is determined solely by the observed data and the assumed data-generating process ---
not by the set of tests that were intended but not performed --- the power of any one
test is unaffected by how many other comparisons are planned, provided each test uses
an independent model \citep{gelman2012, kruschke2015doing}.
% \citet{gelman2012}: Gelman, Hill \& Yajima (2012) is the standard journal reference
% for the claim that Bayesian posteriors typically require no multiple-comparison
% correction when tests are based on independent models.
% \citet{kruschke2015doing}: DBDA2 (Chapter~11) provides the pedagogical treatment.
The precision goal $\omega_{\rm goal}$ and the stopping rule of ePitG therefore apply
unchanged in a multiple-testing context, without the need for correction.

This freedom from multiple-comparison penalties also reshapes how power analysis is
framed in the Bayesian setting.
It is worth distinguishing three types of power analysis that arise in this framework
\citep{kruschke2015doing}.

\textit{Prospective} power analysis is conducted before data collection: given a
hypothesised data-generating distribution (from theory, pilot data, or prior research),
one simulates experiments and asks how often the precision goal $\omega_{\rm goal}$ is
achieved within the budget $N_{\rm max}$.
This is precisely what the analytical formula for $N_{\rm goal}$
(Equation~\ref{eq:pitg_stop_iteration}) provides as a closed-form approximation for the
minimum required sample size within this model; note that $N_{\rm goal}$ is a theoretical
lower bound --- any sequential algorithm requires at least this many observations under
ideal conditions, and ePitG may require additional samples when $\theta_{\rm true}$ lies
near a ROPE boundary (see Section~\ref{sec:trends}).

\textit{Retrospective} power analysis uses the posterior from already-collected data as
the hypothetical data generator to ask whether the completed study was sufficiently
powered. In NHST this quantity is directly determined by the p-value and therefore adds
no new information beyond it \citep{hoenig2001}; in the Bayesian setting it can reveal
the probability of achieving goals other than null rejection.
% \citet{hoenig2001}: Hoenig \& Heisey (2001) demonstrate that observed power in NHST
% is a 1-to-1 function of the p-value and therefore adds no information beyond it ---
% the canonical reference for the redundancy of retrospective NHST power.
\textit{Replication} power asks: if the experiment were repeated exactly, what is the
probability of achieving the goal in the new study, informed by the results of the
first? This is straightforward to compute in a Bayesian framework by using the initial
posterior as the prior for the follow-up, but is difficult to operationalise in NHST,
which has no principled access to a posterior-derived data generator.

A recurring concern about PitG --- and by extension ePitG --- is that the precision
requirement feels too demanding in practice. 
Researchers frequently underestimate the noise in their measurements and are consequently surprised by the sample sizes that
$\omega_{\rm goal}$ implies (J.K.\ Kruschke, pers.\ comm., 2022). This is not a flaw
in the method but a form of epistemic honesty: imprecise posteriors produce inconclusive
results regardless of the algorithm applied; ePitG simply refuses to declare a verdict
until the posterior is genuinely informative. Setting $\omega_{\rm goal}$ thus forces
realistic planning rather than concealing underpowerment behind a false positive or a
silently inconclusive stop.
This discipline is a feature, not a limitation, for any analyst whose conclusions
must rest on genuinely informative data.

The method is most naturally suited to settings where data collection is relatively
cheap and the budget comfortably covers the required sample size: large-scale digital
A/B testing \citep{johari2022}, opinion polling, and automated quality-control pipelines
are typical examples.
% \citet{johari2022}: Johari et al.\ (2022) study continuous monitoring of A/B tests ---
% a canonical high-volume, low-cost data-collection context where precision-based
% stopping is operationally natural and the budget constraint is rarely binding.
For settings where the required sample size is prohibitive --- longitudinal studies,
clinical trials, or expensive policy evaluations --- the framework still serves a
valuable diagnostic role: $N_{\rm goal}$ makes explicit what precision is achievable
within the available budget, enabling an honest assessment of what conclusions the data
can and cannot support.

The ROPE is the most consequential and subjective design input in the framework.
It should be determined from domain knowledge rather than from the data ---
a requirement that forces the researcher to commit to a practically meaningful
effect-size threshold before observing outcomes \citep{kruschke2018}.
% \citet{kruschke2018}: Kruschke's 2018 AMPPS paper is the primary reference for
% ROPE specification in the HDI+ROPE framework, emphasising that the ROPE encodes
% a pre-specified practical equivalence threshold and must be justified from domain
% knowledge rather than chosen to suit the data.
In clinical research the Minimal Clinically Important Difference (MCID) provides a
principled basis \citep{jaeschke1989}; in bioequivalence testing, regulatory guidelines
define the permissible deviation corridor \citep{schuirmann1987}; in industrial quality
control, engineering tolerances serve the same role.
When no domain standard exists, sensitivity analyses across a range of ROPE widths
are recommended before committing to a single value \citep{lakens2018}.

The joint operating characteristics of ePitG --- its false-accept and false-reject
rates as a function of $\theta_{\rm true}$ --- are determined by the interplay of the
ROPE, $\omega_{\rm goal}$, and $N_{\rm max}$, and can be assessed prospectively.
As the Results demonstrate, false-accept rates are negligible except when
$\theta_{\rm true}$ lies within the ROPE boundary region, and false-reject rates are
suppressed by the precision requirement.
A researcher can therefore calibrate the operating characteristics in advance by
verifying via the analytical formula or simulation that the planned $N_{\rm max}$
achieves the target conclusiveness rate at the effect sizes of interest.

One option to increase signal with a limited budget is to incorporate informative priors.
We defer a full treatment of prior selection to future work, noting that informative
priors, where available and well-justified, offer a practical mitigation by contributing
effective pseudo-observations that narrow the starting HDI width and lower the required
sample size \citep{gelman2013bayesian}.
% \citet{gelman2013bayesian}: BDA3 (Chapter 2) establishes the prior-as-pseudo-data
% interpretation for conjugate models: a Beta(a,b) prior is equivalent to having
% previously observed a successes and b failures, directly supporting the claim that
% informative priors contribute effective pseudo-observations.

Three further considerations support the broader adoption of this approach.
First, formally accepting the null via the HDI+ROPE criterion parallels the objective
of frequentist equivalence testing through the Two One-Sided Tests (TOST) procedure
\citep{schuirmann1987, lakens2018}, providing a Bayesian counterpart to a methodology
already accepted in regulatory and applied settings \citep{fda2010bayesian}.
% \citet{schuirmann1987}: The original paper introducing the TOST procedure for
% bioequivalence testing --- the canonical frequentist method for formally accepting
% a null (within a margin), making it the natural comparator for the HDI+ROPE Accept
% verdict.
% \citet{lakens2018}: Lakens et al.\ (2018) is the standard modern tutorial on
% equivalence testing for psychological researchers, providing the methodological
% bridge between TOST and the effect-size framing used here.
% \citet{fda2010bayesian}: The FDA's 2010 Bayesian guidance (\S4.7) explicitly permits
% stopping when the posterior credible interval is ``sufficiently narrow'', the same
% precision principle as PitG. ePitG adds the simultaneous conclusiveness requirement,
% directly addressing the inconclusive-outcome problem the FDA guidance leaves to
% case-by-case design agreement. Citing this document here supports the claim that
% precision-based Bayesian stopping is not merely academic but already embedded in
% regulatory practice.
Second, because $\omega_{\rm goal}$, the ROPE, and $N_{\rm max}$ must all be specified
before data collection begins, ePitG is naturally compatible with pre-registration
standards \citep{nosek2018}, directly reducing the researcher degrees of freedom that
drive selective reporting.
% \citet{nosek2018}: Nosek et al.\ (2018) is the landmark paper establishing
% pre-registration as a standard remedy for selective reporting and p-hacking;
% cited here because ePitG's fully specified stopping rule is directly and
% structurally compatible with pre-registration requirements.
Third, the replication crisis has been partly attributed to underpowered studies whose
imprecise estimates fail to replicate \citep{osc2015, gelman2014}; ePitG addresses this
at the design stage by making precision a non-negotiable stopping criterion rather than
an aspiration --- one that is structurally enforced, since the stopping rule cannot fire
until the precision goal is met.
% \citet{osc2015}: The Open Science Collaboration (2015) documented that a substantial
% fraction of published psychological findings failed to replicate, motivating the search
% for design-stage remedies.
% \citet{gelman2014}: Gelman \& Carlin (2014) specifically link replication failure to
% low power and imprecision (``Type S'' sign errors and ``Type M'' magnitude errors),
% making it the canonical reference for the claim that imprecise estimates fail to replicate.

Three limitations of the present work deserve acknowledgement.
First, the results are sensitive to the three design parameters --- the ROPE,
$\omega_{\rm goal}$, and $N_{\rm max}$ --- all of which must be committed to before
data collection begins.
A narrower ROPE increases the sample size required for acceptance and raises the
inconclusive rate near its boundaries; $\omega_{\rm goal}$ and $N_{\rm max}$ interact
similarly.
Second, the stopping properties are validated empirically only for Bernoulli trials
with a conjugate Beta posterior; the normal approximation underpinning
$N_{\rm goal}$ (Equation~\ref{eq:pitg_stop_iteration}) may require greater caution in
small-sample settings or for highly skewed likelihoods.
Third, the flat prior used throughout contributes no pseudo-observations; an analyst
who encodes a materially incorrect informative prior may bias the posterior in a way
that the precision criterion alone cannot detect.

The extensions to continuous outcomes and two-group comparisons described above are
analytic arguments rather than empirically validated results.
Confirming that the stopping properties demonstrated here for the Bernoulli case carry
over --- in particular the reduction in inconclusive rates and the calibration of
$N_{\rm stop}$ relative to $N_{\rm goal}$ --- requires a dedicated simulation study.
We flag this, together with a formal treatment of informative prior selection, as the
primary directions for future work.

