\documentclass{article}
% use for page size and margins: https://www.overleaf.com/learn/latex/Page_size_and_margins
\usepackage[a4paper, margin=0.7in]{geometry}
% bibliography setup
\usepackage{natbib}
\bibliographystyle{apalike}  % abbrvnat
\setcitestyle{authoryear,open={(},close={)}} %Citation-related commands
% makes color citations
\usepackage[colorlinks=true,urlcolor=blue,citecolor=red,linkcolor=red,bookmarks=true]{hyperref}
% images
\usepackage{graphicx}
\graphicspath{ {./images/} }

% hypter parameter setup
\usepackage{hyperref}
% for table setup
\usepackage{multirow}

% for pseudo code
\usepackage{algorithm}
\usepackage{algpseudocode}

% for math symbols, e.g, \lesssim
\usepackage{amssymb,amsmath}

% to highlight lines of code, as per: https://tex.stackexchange.com/questions/149779/how-can-i-colourfuly-highlight-some-lines-of-an-algorithm-using-algorithm2e
\usepackage{xcolor}
\def\HiLi{\leavevmode\rlap{\hbox to \hsize{\color{yellow!50}\leaders\hrule height .8\baselineskip depth .5ex\hfill}}}


\title{Improved Sequential Hypothesis Testing with
``Enhanced Precision Is The Goal"}
\date{\today}
\author{Eyal A. Kazin}

\begin{document}
\maketitle

\input precision_goal_abstract

\section{Introduction}
\input precision_goal_introduction

\section{Paper Structure}
The paper is organized as follows. In the Methods section, we describe three stop criteria as well as the setup to test on synthetic dichotomous data. In the Results section, we present the results of the synthetic data analysis as well as analytical analysis. In the Discussion section, we discuss the implications of the results. In the Conclusion section, we summarize the findings and suggest future directions.


\section{Methods}
\input precision_goal_methods


\section{Results}\label{sec:results}
\input precision_goal_results


\section{Discussion}\label{sec:dicussion}
\input precision_goal_discussion



\section{Conclusion}\label{sec:conclusion}

Sequential hypothesis testing requires two distinct decisions: \textit{when} to stop
collecting data and \textit{what} to conclude once stopped. Conflating these steps,
as in the HDI+ROPE algorithm, risks stopping on imprecise, unrepresentative posteriors
and produces a systematic false-positive rate ($\sim\!6\%$ in our simulations, even
when $\theta_{\rm true}=\theta_{\rm null}$).
\cite{kruschke2015doing}'s Precision is the Goal (PitG) eliminates this bias by
decoupling the two steps: it stops only once the posterior HDI narrows below a
pre-specified precision goal $\omega_{\rm goal}$, then applies the HDI+ROPE decision
rule. PitG achieves zero false positives, but at the cost of a strikingly high
inconclusive rate --- 63.3\% in the fair-coin case --- because precision and conclusiveness
are not required to coincide.
Moreover, unlike NHST, which can only reject or fail to reject the null,
the HDI+ROPE decision rule enables positive \textit{acceptance} of the null
when the entire HDI falls within the ROPE, a critical advantage for confirmatory
research areas such as bioequivalence, safety testing, and software regression testing
(verifying that a new deployment has not degraded existing behaviour known as do-no-harm).

We have proposed Enhanced Precision is the Goal (ePitG), which re-couples the two
criteria conservatively: data collection continues until the HDI is simultaneously
narrower than $\omega_{\rm goal}$ \textit{and} falls cleanly inside or outside the
ROPE\@. This single change transforms the picture. At $\theta_{\rm true}=\theta_{\rm null}=0.5$,
ePitG achieves a 97.7\% conclusiveness rate with zero false positives, compared to
PitG's 36.7\% --- a $2.7\times$ gain in conclusiveness at a median cost of only 4.7\%
more samples. The efficiency gain is most pronounced near the ROPE boundaries, precisely
where correct decisions matter most; once $\theta_{\rm true}$ moves well outside the
ROPE, ePitG converges to PitG and both stop at $N_{\rm goal}(\theta_{\rm true})$.
These figures correspond to $\omega_{\rm goal}=0.08$, i.e.\ a $\pm 4$ percentage
point margin of error, a standard reporting precision in single-group binomial analyses
such as opinion polling and survey-based research. The qualitative advantage of ePitG over PitG is robust
across precision goals: looser goals (larger $\omega_{\rm goal}$) worsen PitG's
inconclusive rate and amplify ePitG's gain, while tighter goals improve PitG's
conclusiveness at the cost of proportionally larger samples for both methods.

Both precision-based methods share an important analytical property: the expected stop
iteration is given in closed form by
$N_{\rm goal}(\theta,\omega_{\rm goal}) \propto \theta(1-\theta)/\omega_{\rm goal}^2$
(Equation~\ref{eq:pitg_stop_iteration}), enabling prospective planning before any data
are collected. $N_{\rm goal}(\theta_{\rm null})$ is always a theoretical minimum
for the required sample size. Because $\theta(1-\theta)$ is maximised at $\theta=0.5$,
this minimum is largest for the fair-coin null, making it a safe worst-case planning
ceiling. For other nulls, $\theta_{\rm true}$ may lie closer to $0.5$ than
$\theta_{\rm null}$ does, raising the actual minimum above the planned one;
$N_{\rm max}$ should be set generously to cover this (see Discussion).

The framework extends naturally beyond the single-group binomial setting studied here.
The HDI+ROPE decision rule and the precision stopping criterion apply directly to
continuous outcomes by substituting $\sigma^2$ for $\theta(1-\theta)$, and to
two-group comparisons (A/B testing) by using the standard error of the difference as
the precision metric. Compatibility with conjugate posteriors makes the approach
computationally lightweight; pre-registration of $\omega_{\rm goal}$, the ROPE, and
$N_{\rm max}$ before data collection aligns naturally with open-science standards and
eliminates the researcher degrees of freedom that drive selective reporting.
A full empirical evaluation across these settings is left for future work.
To support adoption, all algorithms are implemented in openly available
code\footnote{\textcolor{red}{\textbf{[TODO: insert repo URL]}}
\href{https://github.com/placeholder/precision-goal}{https://github.com/placeholder/precision-goal}},
and an interactive online calculator for prospective sample-size planning via
Equation~\ref{eq:pitg_stop_iteration} is available at
\textcolor{red}{\textbf{[TODO: insert calculator URL]}}
\href{https://placeholder.app/pitg-calculator}{https://placeholder.app/pitg-calculator}.



\appendix

TODO: replicate Figure 18.1 of https://ethanweed.github.io/pythonbook/06.01-bayes.html
for discussion about p-value and Bayes Factor.
\input precision_goal_appendix_hdi
\input precision_goal_appendix_binomial
\input precision_goal_appendix_expected_stop

\section{Useful Equations}
\input precision_goal_useful_equations

\section{Submission Instructions}

Methods Paper—maximum word count: 6500
Methods Papers present an advance likely to make major impact in one or more applied
fields. While theory (e.g. theorems concerning statistical or
learning-theoretic properties) are welcome, this is not essential, but intuition and
understanding of why the method works is important.
We are also very open to theory in a broader sense including examples and conjectures.
Generally, we would expect empirical results to demonstrate effectiveness.
However, in cases where the extent of methodological/conceptual innovation is large
enough, results themselves may be illustrative and need not be of immediate high impact
in any particular applied domain.

Each piece should include:

Unstructured Abstract—maximum word count: 250
Keywords—maximum of 6 and minimum of 5
May include tables and figures—no limit
May include the following back matter sections:
Acknowledgements
Author contributions (with CRediT details)
Conflicts of interest
Funding
Must include the following:
Data availability
References—no limit
Each submission must contain the following sections and use these terms as the first
level section headers: Introduction, Methods, Results, Discussion and Conclusion
(Discussion and Conclusion may be combined).

{\bf Resources}

\href{https://academic.oup.com/rssdat/pages/general-instructions}{RSS Instructions} 

\href{https://academic.oup.com/pages/authoring/books/preparing-your-manuscript/working-in-latex}{RSS Working in \LaTeX}.

{\bf Talking Points to Include}

* Frequentist methods cannot accept null hypothesis:  In the Frequentist case practitioners set the stop criterion that triggers according to a sample to hypothesis p-value and then decide if to reject the null hypothesis (Frequentist methods cannot accept null hypotheses because p-values do not contain enough information).
* Make sure return text returned (and or relevant): "Although our belief is that these methods are applicable to any data type, our focus is on dichotomous data
(Bernouli trials) in order to compare with Kruschke (2015). The advantage of coin flip data is that it is simple to describe analytically enabling rapid tests on synthetic
data" 
* TBD: J.K’s comment about only central value
* $P(\theta|\hat\theta)$

\bibliography{references.bib}

\end{document}