
Sequential hypothesis testing requires two distinct decisions: \textit{when} to stop
collecting data and \textit{what} to conclude once stopped. Conflating these steps,
as in the HDI+ROPE algorithm, risks stopping on imprecise, unrepresentative posteriors
and produces a systematic false-positive rate ($\sim\!6\%$ in our simulations, even
when $\theta_{\rm true}=\theta_{\rm null}$).
\citet{kruschke2015doing}'s Precision is the Goal (PitG) eliminates this bias by
decoupling the two steps: it stops only once the posterior HDI narrows below a
pre-specified precision goal $\omega_{\rm goal}$, then applies the HDI+ROPE decision
rule. In the fair-coin case, PitG achieves zero false positives, but at the cost of a
high inconclusive rate of 63.3\%, because precision and conclusiveness
are not required to coincide.

We have proposed Enhanced Precision is the Goal (ePitG), which re-couples the two
criteria conservatively: data collection continues until the HDI is simultaneously
narrower than $\omega_{\rm goal}$ \textit{and} falls cleanly inside or outside the
ROPE\@. The effect of this single change is substantial. At $\theta_{\rm true}=\theta_{\rm null}=0.5$,
ePitG achieves a 97.7\% conclusiveness rate with zero false positives, compared to
PitG's 36.7\% --- a $2.7\times$ gain in conclusiveness at a median cost of only 4.7\%
more samples. The efficiency gain is most pronounced near the ROPE boundaries, precisely
where correct decisions matter most; once $\theta_{\rm true}$ moves well outside the
ROPE, ePitG converges to PitG and both stop at $N_{\rm goal}(\theta_{\rm true})$.
These figures correspond to a ROPE width of $\Delta_{\rm ROPE}=0.1$ and a precision
goal of $\omega_{\rm goal}=0.08$ --- a $\pm 4$ percentage-point margin of error that
represents standard reporting precision in single-group binomial analyses
such as opinion polling and survey-based research. The qualitative advantage of ePitG over PitG is robust
across precision goals: looser goals (larger $\omega_{\rm goal}$) worsen PitG's
inconclusive rate and amplify ePitG's gain, while tighter goals improve PitG's
conclusiveness at the cost of proportionally larger samples for both methods.
Quantitatively, ePitG's conclusiveness varies by less than one percentage point
($0.972$--$0.979$) across $\omega_{\rm goal}=0.06$--$0.10$, while the
conclusiveness ratio (ePitG/PitG) starts at $1.17\times$ at the tightest
setting and grows rapidly with $\omega_{\rm goal}$.
At $\omega_{\rm goal}=0.10$, PitG yields no conclusive
outcomes (Table~\ref{tab:goal_impact}).

% Unlike NHST (see Appendix~\ref{app:nhst}), which can only reject or fail to reject
% the null, the HDI+ROPE decision rule enables positive \textit{acceptance} of the null
% when the entire HDI falls within the ROPE, a critical advantage for confirmatory
% research areas such as bioequivalence, safety testing, and software regression testing.
% do-no-harm

Both precision-based methods share an important analytical property: the expected stop
iteration is given in closed form by
$N_{\rm goal}(\theta,\omega_{\rm goal}) \propto \theta(1-\theta)/\omega_{\rm goal}^2$
(Equation~\ref{eq:pitg_stop_iteration}), enabling prospective planning before any data
are collected. $N_{\rm goal}(\theta_{\rm null})$ is a guaranteed lower bound
for the required sample size. Because $\theta(1-\theta)$ is maximised at $\theta=0.5$,
this minimum is largest for the fair-coin null, making it the most demanding null for
planning purposes. For other nulls, $\theta_{\rm true}$ may lie closer to $0.5$ than
$\theta_{\rm null}$ does, raising the actual minimum above the planned one;
$N_{\rm max}$ should be set generously to cover this.

The framework extends naturally to single-group continuous data
(Appendix~\ref{app:expected_stop}) and to two-group comparisons such as A/B testing
(Appendix~\ref{app:extensions}); a full empirical evaluation across
these settings awaits a dedicated simulation study.
All algorithms, including these extensions, are already implemented in openly available
code\footnote{\textcolor{red}{\textbf{[TODO: replace repo URL]}}
\href{https://github.com/elzurdo/precision-goal}{https://github.com/elzurdo/precision-goal}},
and an interactive online calculator for prospective sample-size planning via
Equation~\ref{eq:pitg_stop_iteration} is available at
\href{https://r-w-t-y.streamlit.app}{https://r-w-t-y.streamlit.app},
though stopping-property validation for settings beyond the single-group Bernoulli case
remains to be completed.
ePitG is the method of choice whenever a conclusive verdict --- acceptance, rejection,
or an inconclusive outcome --- is required and the cost per observation is low enough
to reach $\omega_{\rm goal}$; the closed-form $N_{\rm goal}$ makes this judgement
transparent before any data are collected.
